\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts, mathtools}
\usepackage{enumitem}
\usepackage{listings}                   % insert code
\usepackage{graphicx}                   % Insert images
%\graphicspath{ {images/} }
\usepackage[letterpaper, margin=1.5cm]{geometry}
\usepackage[singlespacing]{setspace}

\begin{document}
\noindent
\large \textbf{ECSE414 - Intro to Telecom Networks\\Deliverable 1 - Project Description: Onion Routing: Group 10}\\
Authors: C. Garcia La Rotta, D. Liu, E. Zhao, H. Wiltzer, J. Virdee, S.D. Mavroidakos, S. Mashaal\\
September 29, 2017
%Camilo Garcia La Rotta (260657037), Dennis Liu (260581270), Edward Zhao (260690376), Harley Wiltzer (260690006), Jastaj Virdee (260689027), Spiros-Daniel Mavroidakos (260689391), Stuart Mashaal (260639962)
%\large \textbf{ECSE 414 Intro. to Telecom. Networks} \hfill \textbf{Camilo Garcia La Rotta} \textbf{\#260657037} \\
%\large \textbf{Deliverable \#1 - Description}        \hfill \textbf{Jastaj Virdee} \textbf{\#260689027} \\
%\large \textbf{Topic: Onion Routing}                 \hfill \textbf{Dennis Liu} \textbf{\#260581270} \\
%\text{}                                              \hfill \textbf{Edward Zhao} \textbf{\#260690376}\\
%\text{}                                              \hfill \textbf{Harley Wiltzer} \textbf{\#260690006}\\
%\text{}                                              \hfill \textbf{Spiros-Daniel Mavroidakos} \textbf{\#260689391}\\
%\text{}                                              \hfill \textbf{Stuart Mashaal} \textbf{\#260639962}\\

\section*{Project Description}
The goal of this project is to implement and design an Onion Routing protocol,
which ideally allows for users to communicate completely anonymously over the
internet. Communication with Onion Routing involves having servers on a network that some
data is passed through with multiple layers of encryption. These encryption layers get decrypted as
the message is passed along throughout the intermediate servers in the path.
However, as opposed to proxy servers for example,
the layered encryption ensures that no nodes along the
message path are aware of who the sender was, so it is impossible to determine
if a particular sender ever actually sent a message. Our Onion Routing
system will support encryption on bidirectional communication to achieve this
anonymity.\\

%Anonymity is an important feature of computer systems when communicating over a network. This project involves implementing a simplified version of onion routing. The system will include features of message encryption, redirection through intermediate nodes, and bi-directional communication. \\

\noindent Performance of the system will also be assessed via simulation. A network topology which mimics characteristics of the internet will be used. Onion routing will be evaluated by comparing the lengths of routes taken by a packet using onion routing to one using shortest-path routing. Additional delay will also be included to calculate the total price of anonymity.

\section*{Methodology}

The Onion Routing Protocol will be implemented with several independent routers (nodes)
communicating via TCP packets.  For all $N$ nodes, each node $n_i$ has
an asymmetric cryptographic key pair $(pub_{i},priv_{i})$ and an IP address $a_i$.  Additionally, a special
server called the Directory Node contains the information $\{(a_i, pub_i) \forall i \in [\![1..N]\!]\}$.\\

\noindent Say a sender $\mathcal{S}$ wishes to send a request (and receive a response)
from some destination $\mathcal{D}$.  Firstly, $\mathcal{S}$ connects to the Directory Node
and requests a path $\mathbf{P}$ through the network. The Directory Node then generates
$\mathbf{P}$, a random and ordered subset of the onion-net's $N$ nodes where $|\mathbf{P}| \leq N$.  For each node
$n_j \in \mathbf{P}$, the Directory Node negotiates using the corresponding
$pub_j$ and its own private key, thereby producing a symmetric key $sym_j$.  The Directory
Node then constructs a packet containing $\{(a_j, sym_j) \forall j \in [\![1..|\mathbf{P}|]\!]\}$ and
encrypts it with the public key corresponding to $\mathcal{S}$, and sends the cipher to $\mathcal{S}$.\\

\noindent Now, $\mathcal{S}$ decrypts the cipher with his private key. He creates the
request he wishes to send to $\mathcal{D}$, and encrypts with each $sym_j$
successively, but in reverse order (so the first $sym_j$ he encrypts with is $sym_{|\mathbf{P}|}$, which corresponds
to the last node in the path). Before encrypting with each $sym_j$, a header
indicating which node to send to next is prepended so that each node can
determine where to send the packet after decrypting. $\mathcal{S}$ proceeds to
send this many-layered ``onion'' of ciphers to the first node in the path.\\

\noindent Each intermediate node $n_j$ behaves according to the exact same protocol. Upon receiving
a packet, a node $n_j$ decrypts the packet with its symmetric key to expose $a_{j+1}$, the
address of the next node $n_{j+1}$ in the path.  After sending the packet to $n_{j+1}$, $n_j$
waits for a response packet.  When a response packet is received, $n_j$ encrypts the response with
$s_j$ and sends the packet to $n_{j-1}$.  When $\mathcal{S}$ receives the response, he decrypts
with each symmetric key successively (now in forward order), and can then read the response.\\

\noindent All nodes will be implemented as TCP servers programmed with the Python programming
language using the Flask framework to handle concurrent requests.  The Vagrant tool will be
used to automate the creation of virtual machines which will simulate the nodes.  Additionally,
to save processing power, the Directory Node will run locally on the sender's machine for the
purposes of the simulation.\\

\noindent Furthermore, the NTRU cryptoscheme will be considered and investigated to
provide key exchange for communicating the $s_i$ keys, and can maintain
security against quantum opponents.

\section*{Testing}
The goal of the project is to achieve a minimalist implementation of onion
routing and perform analysis of its performance via simulation. As such,
testing of this project should be divided into two sections:
\begin{enumerate}
	\item \textbf{Verify and validate the onion routing implementation:} We
		will follow a Test Driven Development (TDD) paradigm. Writing test
		cases first, then deriving the unit tests through equivalence
		partitioning and finally writing the necessary code for all the tests
		to pass. Throughout this iterative process we will rely on Continuous
		Integration (CI) to efficiently manage all the source code generated by
		each sub-team. The concept of pair programming will be leveraged in
		order to equally subdivide the tasks among the group and to ensure
		regular code reviews are performed on the code base. With respect to
		the application testing, we shall focus on three main aspects of onion
		routing: \underline{bidirectional communication}, \underline{encryption
		of data through nodes} and \underline{randomized path selection}. Each
		of these characteristics will be unit tested with virtual machines and
		after satisfying our requirements they will be undergo integration
		testing. In order to efficiently replicate the development and testing
		environment across the machines of each team member, Vagrant will be
		used to build and maintain the portable virtual development
		environments.
	\item \textbf{Analyze the performance of the application through
		simulation:} There will be two tools that will be used, one is Nmap
		which provides a broader overview of the network and Wireshark to
		examine the packets transferred between nodes. We will be using Nmap
		for testing enumeration of network components and available application
		layer protocols at end hosts. It will also be used to identify any
		vulnerabilities in the network and to ensure the ports are connected to
		the correct hosts. Wireshark is used to test encryption requirements,
		provide an analysis of the chosen network and ensure contiguous nodes
		know the adjacent source destination and not the global ones. For
		further testing, we may use the mentioned tools such as Brite or Orbis
		to generate network topology to simulate characteristics in the
		internet.

% As for the second section of testinng (performance) we gotta find some tools for network testing (i.e. nmap, wireshark) and talk about
% how we will benchmark those tests ina very high level manner

\end{enumerate}

\section*{Work Division}
The work for this project will be divided into two main subteams, one of which
will be the development subteam, and the other will be the testing subteam. As
it stands, Camilo, Harley, Spiros-Daniel, and Stuart will make up the
development subteam, and Dennis, Edward, and Jastaj will make up the testing
subteam. It has been decided that each team member will document his own work,
and Harley has volunteered to manage and compile the documentation that
everyone writes. Furthermore, due to the difficulty of testing this system,
Spiros-Daniel has volunteered to help out the testing team, so that the testing
team can have assistance with testing out the more intricate parts of the
system.\\\\
The development team will be in charge of developing the code and the software
and network architectures. Furthermore, to follow a TDD paradigm, the
development team will be in charge of writing unit tests for the features that
they will be implementing.\\
The testing team will be in charge of conducting thorough integration and
system tests that should reveal the behavior of the system under ordinary and
stressful circumstances. The testing team will then report bugs or improvement
ideas to the development team as they find them. Furthermore, the testing team
will be in charge of setting up and managing the Continuous Integration of our
software.

%\section*{Work Division}
%\textbf{Development and Unit Testing:}
%	\begin{itemize}
%    \item Camilo Garcia La Rotta
%    \item Harley Wiltzer
%    \item Spiros-Daniel Mavroidakos
%    \item Stuart Mashaal
%	\end{itemize}
%
%\noindent \textbf{Component and System Testing:}
%	\begin{itemize}
%    \item Edward Zhao
%    \item Jastaj Virdee
%    \item Dennis Liu
%	\end{itemize}

\end{document}
